---
title: Beer Market Project
subtitle: "Beer Market Project: What is the most common beer brand based on buyertype and degree"
author: 
  - Morgan Bush

toc: true
toc-title: "Table of Contents"
toc-depth: 2
number-sections: true

fig-width: 9

execute:
  code-tools: true
  message: false
  warning: false

from: markdown+emoji
---
```{r setup}
#| include: false
library(tidyverse)
library(skimr)
library(ggthemes)
library(hrbrthemes)

theme_set(theme_ipsum()+
          theme(strip.background =element_rect(fill="lightgray"),
                axis.title.x = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(10,0,0,0)),
                axis.title.y = 
                  element_text(angle = 0,
                               size = rel(1.33),
                               margin = margin(0,10,0,0))
                )
          )
```



# Introduction

About this project :clap:

```{r}
beer_markets <- read_csv("https://bcdanl.github.io/data/beer_markets_all.csv")
```


# Data

This is data.frame beer_market contains a sbset of beer data.


## Summary Statistics


```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(beer_markets) 
```


```{r}
skim(beer_markets) %>% 
  select(-n_missing)
```



```{r}

brandchoice <- beer_markets |>
  count(brand)
ggplot(data=beer_markets) +
  geom_bar(mapping =aes(y =brand, fill= buyertype))

```

In this bar chart we can see the relationship between the number of males, females, or married by of the brands including Natural Light, Miller Light, Coors Light, Busch Light, or Bud light. In the chart we can see the most popular brand for married to purchase is Bud Light. The brand that is least purchased for females is Busch Light. 

```{r}
brand_buyertype <- beer_markets |>
  count(brand, buyertype)

rmarkdown::paged_table(brand_buyertype) 

```

```{r}
brand_degree <- beer_markets |>
  count(brand, buyertype, degree)

rmarkdown::paged_table(brand_degree) 


ggplot(brand_degree,
       aes(x=n, y=brand, fill = buyertype))+
  geom_col(position = "dodge") +
  facet_wrap(degree ~ .)
```

In this chart we are looking out the relationship between brand, buyertype, and degree based on the number of buyers for each buyertype. As we look at this chart we can see the most Bud Light is purchased by married in HS. 


```{r}
ggplot(brand_degree,
       aes(x=n, y=brand, fill = buyertype))+
  geom_col(position = "fill") +
  facet_wrap(degree ~ .)
```

In this chart we are also looking at the relationship between brand, buyertype and degree. The difference between the one previous is that this is measured by percentage out of 1.00. The most popular brand in college for married is Busch Light. The least popular brand in none(no degree) for married is Busch Light.

```{r}
beer_state <- 
  beer_markets %>% 
  count(state) %>% 
  arrange(-n)
rmarkdown::paged_table(beer_state) 


beer_state
```

```{r}
#| fig-height: 25
brand_state <- beer_markets |>
  count(brand, state, buyertype)
ggplot(brand_state,
       aes(x=n, y=brand, fill = buyertype))+
  geom_col(position = "dodge") +
  facet_wrap(state ~ ., ncol = 3)

```
In this chart 

```{r}
#| fig-height: 25
#| 
ggplot(brand_state,
       aes(x=n, y=brand, fill = buyertype))+
  geom_col(position = "fill") +
  facet_wrap(state ~ ., ncol = 3)

```

On this chart we are looking at the percentages of buyer types based on the brand and the state they buy in. In New York the highest percentage of females buy Natural Light Beer compared to the lowest percentage of females buy Coors Light Beer.  






